Datasheet for 'New York Bridge 2016

### 2024-12-03 other/datasheet/datasheet.qmd
Update contact link

For questions regarding the dataset hosted on DASL, users can reach out by filling out the contact form available [here](https://dasl.datadescription.com/datafile/new-york-bridges-2016/?_sf_s=Bridge&_sfm_cases=4+59943). This ensures that inquiries about the archived dataset can be addressed promptly. However, for the latest data or updated versions, users are encouraged to visit the Open Data NY platform, which continues to provide up-to-date datasets on bridge conditions in New York State.

>>>>

For questions regarding the dataset hosted on DASL, users can reach out by filling out the contact form available [here](https://datadescription.com/). This ensures that inquiries about the archived dataset can be addressed promptly. However, for the latest data or updated versions, users are encouraged to visit the Open Data NY platform, which continues to provide up-to-date datasets on bridge conditions in New York State.
